---
title: "Primary productivity in the Arctic: modeling products from Takuvik"
subtitle: "🛰️ <br><br>Presented by Philippe Massicotte"
author: "In collaboration with (*no specific order*): Maxime Benoît-Gagné, Simon Bélanger, Emmanuel Devred, Atsushi Mastuoka, Marcel Babin, Marie-Hélène Forget, Jean-Thomas Baillargeon, Eric Rehm, Mathieu Ardyna"
date: "2020-02-11--2020-02-12 (Ottawa, Canada)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [xaringan-themer.css, styles.css]
    self_contained: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  out.width = "100%",
  fig.align = "center",
  # fig.width = 8,
  # fig.asp = 0.618, # 1 / phi
  fig.show = "hold",
  dev = "png",
  dpi = 600,
  message = FALSE,
  warning = FALSE,
  echo = FALSE
)
library(tidyverse)
library(ggpmthemes)
library(fontawesome)
library(knitr)
library(kableExtra)
library(patchwork)
library(ggtext)
library(sf)

theme_set(theme_poppins(base_size = 12))
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
duo(
  code_font_family = "Fira Code",
  code_font_url = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css",
  text_font_google = google_font("Questrial"),
  inverse_background_color = "#ABB7B7",
  inverse_text_color = "#3c3c3c",
  inverse_header_color = "#3c3c3c",
  background_color = "#3c3c3c",
  header_color = "#B2CCE5",
  title_slide_text_color = "#3c3c3c",
  title_slide_background_color = "#ABB7B7"
  # Yanone Kaffeesatz
)
```

class: my-one-page-font, inverse, center, middle

# The vertical distribution of underwater light in open water

An overview

---

# Ideas

- Two products (ppv0 and ppv1)

- Map with colored region 45N +

- Verticallity (Ardyna paper)

- Show vertical profiles of Chla (from ppv1, find one on the NAS)

- Validation of the algorithm (round-robin paper)

- Work in progress (show some early results)
    - Show a figure with decreasing SIC and that will likely result in increasing PP for some region.
    - Show the WWF regions (allow to do regional budget)
    - Talk about CCI/GC (which one we used)

- Make the data available as soon as possible

---

class: my-one-page-font, inverse, center, middle

# Spatial extent

45+, pixel resolution, etc.

---

class: my-one-page-font, inverse, center, middle

# Model specifications

---

# Model specifications

- Chlorophyll-a inputs: CCI (can be easily modified - use Juan inputs)

    - Image with all the sensors used in CCI
    - merged MERIS, Aqua-MODIS, SeaWiFS and VIIRS 

- Temporal resolution

    - Daily, between 2003-2018 (15 years of continuous data)

---

class: my-one-page-font, inverse, center, middle

# Outgoing project

---

# The phenology of primary production

27 regions

```{r wwf_regions, fig.height=3.5, dev.args=list(bg="transparent")}
wm <- rnaturalearth::ne_countries(returnclass = "sf", scale = "medium") %>%
  st_crop(
    xmin = -180,
    xmax = 180,
    ymin = 45,
    ymax = 90
  )

wwf <- st_read("//Desktop-main/d/work-ulaval/projects/phenology_pp/data/Carte WWF source/RACER_Study_Units_160210_Mar.shp", quiet = TRUE)

wm %>%
  ggplot() +
  geom_sf(size = 0.25, fill = "gray50", color = "white") +
  geom_sf(data = wwf, aes(fill = Unique_ID), show.legend = FALSE, size = 0.25, color = "white") +
  coord_sf(crs = st_crs(wwf)) +
  rcartocolor::scale_fill_carto_c(palette = "Teal") + 
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
```

